NN_Accel_Heading

### 2024-03-07 Fish Data Analysis/NN_Accel_Heading.qmd
changing angle calculation

tester_model <- lm(Fish1_Yaw_Heading_PS ~ sin(Angle_Rads):Ablation:Darkness, data = fish_data_nn_model)

@@

ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = mean_turn, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  #geom_smooth(se = F)+
  #geom_line(aes(y = sin_pred)) +
  #geom_line(alpha = 0.75) +
  #geom_smooth(se = F, method = glm, formula = y ~ sin(x))+
  geom_line(aes(y = predict(heading_ps_angle_step,
                    newdata = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Angle_Rads = angle_bins))), size = 1)+
  theme_classic() +
  xlab("direction of neighbour (rad)") +
  ylab("focal fish turning angle (rad/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = c("-π","-3π/4","-π/2","-π/4","0","π/4","π/2","3π/4","π"))+
  labs(color = "Sensory Conditions")

>>>>

tester_model <- lm(Fish1_Yaw_Heading_PS ~ sin(Ablation+Darkness+Angle_Rads), data = fish_data_nn_model)

@@

ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = mean_turn, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  #geom_smooth(se = F)+
  #geom_line(aes(y = sin_pred)) +
  #geom_line(alpha = 0.75) +
  #geom_smooth(se = F, method = glm, formula = y ~ sin(x))+
  geom_line(aes(y = predict(tester_model,
                    newdata = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Angle_Rads = angle_bins))), size = 1)+
  theme_classic() +
  xlab("direction of neighbour (rad)") +
  ylab("focal fish turning angle (rad/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = c("-π","-3π/4","-π/2","-π/4","0","π/4","π/2","3π/4","π"))+
  labs(color = "Sensory Conditions")
